---
title: "Stargazer Tests"
author: "Brooks Ambrose"
date: "August 15, 2016"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
bibliography: ../d2016-.bib
---

```{r init,include=F,eval=T}
#csl: asa.csl
#bibliography: d2016.bib
#documentclass: uclathes
#classoption: PhD
#cls: uclathes.cls
#bibliography: d2016-.bib


#\usepackage[labelfont=bf,justification=justified,singlelinecheck=false]{caption}
cat('\014')
rm(list=ls())
#source('/Users/bambrose/Dropbox/GitHub/manuscripts/resources/d2016-init.R')
source(dir(pattern='d2016-glossary.R',recursive=T))
require(ngramr)
require(ggplot2)
require(stargazer)
require(magrittr)
ev=F
ec=F
fig='Figs/ch0/'
tab='Tabs/ch0/'
knitr::opts_chunk$set(eval=T,fig.path=fig,fig.align='center',comment=NA)
c.f.s.o.def=T #check for saved output
```

```{r t-stages1,results='asis',eval=T}
t.stag1<-data.frame(
	Stage=bold(c('1 Prototyping','2 Assemblage','3 Facilitation','4 Accumulation'))
	,Sensemaking=c('Obsession','Recognition','Mastery','Competition')
	,Control=c('Private','Peer','Provider','Professional')
	)

sg(t.stag1,title='Stages',col.align=c('ccc','lll'))
```

```{r t-stages2,results='asis'}
t.stag2<-data.frame(
	Mechanism=c('Cultural','Cognitive','Social')
	,Aparadigmatic=c('Charisma \\cite{Gustin:1973ul}','Chaos','Autonomy')
	,Preparadigmatic=c('Genre','Schema','Heteronomy')
	,Paradigmatic=c('Paradigm','Schema','Heteronomy')
	,Postparadigmatic=c('','','')
)

sg(t.stag2,title='stages',col.align = c('ccccc','lllll'),add.lines=) 
```

\begin{table}[!htbp]
  \centering
  \caption{Mechanisms Operating at each Stage of Development}
  \label{}
\begin{tabular}{@{\extracolsep{5pt}}llll}
\\[-1.8ex] \hline \\[-1.8ex] 
          & \multicolumn{3}{c}{Stage}                                       \\ \\[-1.8ex] \cline{2-4} \\[-1.8ex]
Mechanism & Aparadigmatic & Preparadigmatic & Paradigmatic \\ \\[-1.8ex] \hline \\[-1.8ex]
Cultural  & Charisma \cite{Gustin:1973ul} [@Gustin:1973ul]      & Genre           & Paradigm     \\
Cognitive & Chaos         & Schema          & Schema       \\
Social    & Autonomy      & Heteronomy      & Heteronomy   \\ \\[-1.8ex] \hline \\[-1.8ex]
\multicolumn{4}{l}{}                                                       
\end{tabular}
\end{table}
